Pool Model - A unified Mathematical\\ Modelling Framework for Food Science

### 2025-09-03 paper/pool_model.tex
write first part of introduction

\paragraph{General Introduction to Bacterial Consortia}
\begin{itemize}
    \item Complex system; many players (cell-types, interactions)
    \item processes on different scales (population, cellular, molecular, gene-level)
    \item Food Safety, Production
    \item Healthcare: Drug development
    \item Environmental Sustainabiliy
\end{itemize}
Motivation: general, flexible approach for bacterial systems that allows easily modify the system depending on processes on different scales.
Allows us to describe the processes within populations using different bacterial states as well as interactions between different populations using ODEs.

>>>>

% \paragraph{General Introduction to Bacterial Consortia}
% \begin{itemize}
%     \item Complex system; many players (cell-types, interactions)
%     \item processes on different scales (population, cellular, molecular, gene-level)
%     \item Food Safety, Production
%     \item Healthcare: Drug development
%     \item Environmental Sustainabiliy
% \end{itemize}
% Motivation: general, flexible approach for bacterial systems that allows easily modify the system depending on processes on different scales.
% Allows us to describe the processes within populations using different bacterial states as well as interactions between different populations using ODEs.

Bacterial consortia are highly complex systems which consist of multiple distinct cell types.
The underlying processes are interconnected with each other and occur on all scales, ranging from
population-based dynamics of colony growth over molecular processes such as metabolism to gene
expression.
Bacterial communities are ubiquitous and even able to survive under extreme conditions, making them
virtually omnipresent around any living system.
They play an especially important role within the context of food safety and production
being a key contributor to the spoilage of food products as well as fermentation processes.
Furthermore effects such as biofilm formation can hinder drug treatment by shielding the bacterial
colony from antibiotic substances or immune response of the organism.
The natural bacetrial processes are a crucial part of our planets ecosystem, being responsible for
tasks such as nutrient cycling, decomposition of organic matter and oxygen production.
It is of great interest to understand the dynamics of these various processes.
